\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-05-19 paper.tex
Rephrase, integrate SHARY section, based on Rachid's contribution

While parts of the architecture ({\sc Spark}, {\sc Oro}) have been deployed with
external execution controllers (like {\sc Cram}~\cite{Beetz2010} or the BERT
platform~\cite{Lallee2010b}, as reported in~\cite{Lemaignan2010}), we have also
developed dedicated robot controllers which integrate the whole stack introduced
in Figure~\ref{fig|archi}. {\sc Shary}~\cite{clodic2008shary} is the main one,
written in the \emph{Procedural Reasoning System} language~\cite{Ingrand1996}.
We have also developed the Python-based {\sc pyRobots} collection of tools to
provide a large set of high-level actions and an event-based architecture well
suited for prototyping.  They both rely on deep integration with the knowledge
base that serves as the primary source of semantics for decision making.

One of the main role of {\sc Shary} is to control the elaboration and execution
of shared plans~\cite{Grosz1996,Clark1996,Kemp2007}. This means essentially
contex-based refinement and robot actions execution as well as monitoring of
those achieved by its human partner~\cite{Breazeal2003}. The challenge is to
build such abilities in a generic way, and to provide several levels of
parametrization allowing to adapt to various environments, and various levels of
involvement of the robot ranging from teammate behaviour to assistant or
proactive helper.  Depending on this, the robot controller invokes the various
human-aware planners and will react to events detected at ORO level.

SHARY’S originality, as a supervision system, lies in its ability to take into
account not only the task achievement but also communication and monitoring
needed to support interactive task achievement ~\cite{Rich1997,Sidner2005} in a
flexible way. SHARY allows to link action execution to more or less elaborated
“communication policies” in order to produce signals towards the human and to
react to human action.

A communication act is the central notion in the formalism. It plays the role of
transition condition. Consequently, a communication act represents an
information exchange between the two agents. This exchange can be realized
through dialog or by an expressive motion or a combination of the two. It
enables each agent to communicate his belief about the task to be realized in
order to share mutual knowledge and to synchronyze their activities.  This is
done through real-time task-based situation assessment achieved by the
combination of SPARK monitoring processes and ORO inference mechanisms
\cite{fiore2014}.

>>>>

While parts of the architecture ({\sc Spark}, {\sc Oro}) have been deployed with
external execution controllers (like {\sc Cram}~\cite{Beetz2010} or the BERT
platform~\cite{Lallee2010b}, as reported in~\cite{Lemaignan2010}), we have also
developed dedicated robot controllers which integrate the whole stack introduced
in Figure~\ref{fig|archi}. {\sc Shary}~\cite{clodic2008shary} is the main one,
written in the \emph{Procedural Reasoning System} language~\cite{Ingrand1996}.
We have also developed the Python-based {\sc pyRobots} collection of tools to
provide a large set of high-level actions and an event-based architecture well
suited for prototyping.  They both rely on extensive integration with the knowledge
base, that serves as the primary source of semantics for decision making process.

One of the main role of {\sc Shary} is to control the elaboration and execution
of shared plans~\cite{Grosz1996,Clark1996,Kemp2007}. This means essentially
context-based refinement and robot actions execution, as well as monitoring of
those achieved by its human partner~\cite{Breazeal2003}. The challenge is to
build such abilities in a generic way, and to provide several levels of
parametrisation allowing to adapt to various environments, and various levels of
involvement of the robot ranging from teammate behaviour to assistant or
proactive helper.  Depending on this, the robot controller invokes the various
human-aware planners and will react to events detected at {\sc Oro} level (as
described below).

{\sc Shary}'s originality, as an execution control system, lies in its ability
to take into account not only the task achievement but also communication and
monitoring needed to support interactive task
achievement~\cite{Rich1997,Sidner2005} in a flexible way. {\sc Shary} allows to
link action execution \emph{communication policies} in order to produce signals
towards the human and to react to human actions. The \emph{communication act} is
the central concept in this formalism. It plays the role of transition
condition, and, as such, represents an information exchange between the two
agents. This exchange can be realised through dialogue, by an expressive motion
or a combination of the two. It enables each agent to communicate their beliefs
about the task to be achieved, in order to share mutual knowledge and to
synchronise their activities.  This is done through real-time task-based
situation assessment achieved by the combination of {\sc Shary} monitoring
processes and {\sc Oro} inference mechanisms~\cite{fiore2014}.
